Ball path curvature and in-game free throw shooting proficiency in the National Basketball Association

### 2025-06-22 articles/arxiv/paper.tex
Updates from Overleaf

@@

    Interestingly, the relationship between max curvature and shooting performance runs counter to the findings of \citet{slegers_role_2024}. We find that max curvature is negatively associated with FT\%. However, the primary implications of the overall results are similar. Placing greater emphasis on the latter part of the ball's trajectory---where control and release are most critical---improves the model's ability to explain variation in shooting accuracy. The present results reflect free throw shooting by NBA players in game conditions while the prior results reflect three-point jump shooting by lower-level professionals in practice conditions.

>>>>

    \subsection{Sample Size Estimation and Justification}
      This study is exploratory in nature and is not conducted with planned specific hypothesis tests. Therefore, we report a sensitivity power analysis to quantify the minimum effect size detectable given the data sample size and model assumptions.

      We analyzed 515 515

@@

    Interestingly, the relationship between max curvature and shooting performance runs counter to the findings of \citet{slegers_role_2024}. We find that max curvature is negatively associated with FT\%. The present results reflect free throw shooting by NBA players in game conditions while the prior results reflect three-point jump shooting by lower-level professionals in practice conditions. Despite this discrepancy, the primary implications of our overall results are similar to those of past work. Placing greater emphasis on the latter part of the ball's trajectory---where control and release are most critical---improves the model's ability to explain variation in shooting accuracy.
